Avoiding the Global Sort: \break A Faster Contour Tree Algorithm

### 2017-01-03 paint-contour-tree.tex
small changes

\begin{definition} \label{def:color-set} Fix a painting $\chi$ and vertex $v$.
\begin{asparaitem}
	 \item For every maximal connected component $Y$
     of $\MM^+_v$, the set of all edges connecting $v$ to $Y$
     is called an \emph{up-star}.
	 \item A vertex $v$ is \emph{touched by color $c$} if $v$ is incident to a $c$-colored
	 edge with $v$ at the lower endpoint. For $v$, $\col(v)$ is the set of colors that touch $v$.
	 \item A color $c \in \col(v)$ \emph{fully touches} $v$ if all edges in an up-star are colored $c$.
	 \item For any maximum $x\in X$, we say that $x$ is both touched and fully touched by $\chi(x)$.
\end{asparaitem}
\end{definition}

@@

\section{Divide and conquer through contour surgery} \label{sec:surgery}
Now that we have an efficient join tree algorithm, we now describe how to 
reduce computing the contour tree to computing the join tree, as discussed in \Sec{approach}.
Specifically, in this section we first describe our basic cutting tool, which we call contour surgery.
In \Sec{rain} we then describe how we use this tool to cut the surface into so called extremum dominant pieces 
where computing the contour tree reduces to computing the join tree, and this equivalence is proven in \Sec{extreme}. 
The pieces were create are technically not simplicial complices,
in that each piece may have facets that not simplices. We may
create facets of larger size than the dimension. These can
easily be completeed into simplicial complices, though we do not
explicitly need this. For ease of exposition, we do not explicitly
perform this step in our algorithm.

>>>>

\begin{definition} \label{def:color-set} Fix a painting $\chi$ and vertex $v$.
\begin{asparaitem}
	 \item For each maximal connected component $Y$
     of $\MM^+_v$, the set of all edges connecting $v$ to $Y$
     is called an \emph{up-star}. (Note $v$ has at most two up-stars, as Morse up-degree is at most 2 by assumption.)
	 \item A vertex $v$ is \emph{touched by color $c$} if $v$ is incident to a $c$-colored
	 edge with $v$ at the lower endpoint. For $v$, $\col(v)$ is the set of colors that touch $v$.
	 \item A color $c \in \col(v)$ \emph{fully touches} $v$ if all edges in an up-star are colored $c$.
	 \item For any maximum $x\in X$, we say that $x$ is both touched and fully touched by $\chi(x)$.
\end{asparaitem}
\end{definition}

@@

\section{Divide and conquer through contour surgery} \label{sec:surgery}
Now that we have an efficient join tree algorithm, we now describe how to 
reduce computing the contour tree to computing the join tree, as discussed in \Sec{approach}.
Specifically, in this section we first describe our basic cutting tool, which we call contour surgery.
In \Sec{rain} we then describe how we use this tool to cut the surface into so called extremum dominant pieces 
where computing the contour tree reduces to computing the join tree, and this equivalence is proven in \Sec{extreme}. 
The pieces we create are technically not simplicial complexes,
in that each piece may have facets that are not simplices. We may
create facets of larger size than the dimension. These can
easily be completed into simplicial complexes, though as we do not
need this, for ease of exposition, we do not explicitly
perform this step in our algorithm.
